On the Design, Use and Removal of Eval in R

### 2020-08-20 inst/paper/main.tex
Case study section: base
Basic text for number of evals

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

@@

@@

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{xspace}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\newcommand{\missingNumber}{\textcolor{red}{XX}\xspace}
\newcommand{\missingPercentage}{\textcolor{red}{XX\%}\xspace}
\newcommand{\missingTable}{\textcolor{red}{XXTable}\xspace}
\newcommand{\missingGraph}{\textcolor{red}{XXGraph}\xspace}
\begin{document}

@@

In our corpus eval is called \missingNumber times out of \missingNumber
total calls to all R functions. This is merely \missingPercentage of the total
number of calls. \missingTable breaks down the number of calls and callsites for
the four kinds of eval functions from the three source; core R, packages and
Kaggle code.

The core R packages are the biggest consumers of eval. Majority of calls,
\missingPercentage, originate from the core R packages. Kaggle code, which is
end-user code, has merely \missingNumber calls to eval.

Of the \missingNumber packages in our corpus, only \missingNumber packages call
eval. \missingTable shows the number of calls to eval made by the ten most
frequent callers to eval. \missingNumber packages account for over
\missingPercentage calls to eval.

\missingGraph shows the distribution of number of callsites to eval across these
packages. \missingNumber packages have a single eval callsite.

@@

\subsubsection{A taxonomy of \texttt{eval}}

We first classify \texttt{eval} depending on the resolved expression, \emph{i.e.} the first argument of \texttt{eval} after all possible function calls and symbol resolution in it have been executed.

@@

\section{Case studies}

\subsection{\texttt{base}}
